\section{The Illustris Simulation}

\label{sec:illustris}The Illustris Project is a series of large-scale
cosmological hydrodynamical simulations of galaxy formation \citep{vogelsberger2014properties}.
The simulation consists of large cosmological situations in a periodic
box with $106.5\;{\rm Mpc}$, simulated with different physics at
different resolutions. It assumes a standard flat $\Lambda$CDM cosmology
with $\Omega_{m,0}=0.2726$, $\Omega_{\Lambda,0}=0.72746$, $\Omega_{b,0}=0.0456$,
and $H_{0}=70.4$ km s$^{-1}$ Mpc$^{-1}$ from the Wilkinson Microwave
Anisotropy Probe 9-year data release \citep{hinshaw2013nineyear}.

In the Illustris simulations, collisionless black hole particles with
a seed mass of $1.42\times10^{5}M_{\odot}$ are placed in dark matter
halos of mass greater than $7.1\times10^{10}M_{\odot}$\citep{sijacki2014theillustris}.
The black hole seeds are allowed to grow through gas accretion or
through mergers with other black holes. The black hole seeds are allowed
to grow through gas accretion. At $z=0$, there are 32,542 black holes
in total with 3965 black holes more massive than $10^{7}M_{\odot}$.

\begin{comment}
In the Illustris simulations, collisionless black hole particles with
a seed mass of $1.42\times10^{5}M_{\odot}$ are placed in dark matter
halos of mass greater than $7.1\times10^{10}M_{\odot}$\citep{sijacki2014theillustris}.
The black hole seeds are allowed to grow through gas accretion or
through mergers with other black holes. The black hole seeds are allowed
to grow through gas accretion, parametrized in terms of Eddington
limited Bondi-Hoyle-Lyttleton (BHL)-like accretion (\citet{bondi1952accretion,bondihoyle1044}),
or through mergers with other black holes. BHL is a non-spherical
accretion flow which develops when a compact object moves relative
to a uniform gas cloud. The BHL accretion rate on the black hole is
given by

\begin{equation}
\dot{M}_{B}=\frac{4\pi G^{2}M_{BH}^{2}\rho}{(c_{s}^{2}+v^{2})^{3/2}},
\end{equation}


where $\rho$ and $c_{s}$ are the density and sound speed of the
gas, respectively, $\alpha$ is a dimensionless parameter, and $v$
is the velocity of the black hole relative to the gas. Then, the accretion
is limited to the Eddinton rate,

\begin{equation}
\dot{M}_{Edd}=\frac{4\pi G^{2}M_{BH}m_{p}}{\epsilon_{r}\sigma_{T}c},
\end{equation}


where $m_{p}$ is the proton mass, $\sigma_{T}$is the Thompson cross-section
and $\epsilon_{r}$is the radiative efficiency. The radiaitve efficiency
is related to the radiated bolometric luminosity, $L_{B}$, and accretion
rate, $\dot{M}_{BH}$, by
\begin{lyxcode}
\begin{equation}
\epsilon_{r}=\frac{L_{r}}{\dot{M}_{BH}}
\end{equation}

\end{lyxcode}
This simply gives the mass to energy conversion efficiency set by
the amount of energy that can be extracted from the innermost stable
orbit of an accretion disk around a black hole.
\end{comment}
